\unnumberedchapter{Acknowledgments} 
\chapter*{Acknowledgments} 

First, I would like to acknowledge all those at the University of Tennessee who helped me succeed during my graduate studies. I thank my classmates for their camaraderie as we solved difficult problems during our coursework. I also thank my instructors: I have frequently referred to notes from Steven Johnston’s course in mathematical methods, Kenneth Read’s course in numerical methods, and Christian Batista’s course in statistical mechanics. I especially thank Dr. Batista for his dedication to his graduate students during three semesters of study, including holding extra recitations, providing Krispy Kreme donuts to help us through long exams, and scoring the most goals on our intramural soccer team. Outside of Tennessee, I thank Alex Bogacz, Geoffrey Krafft, and Yuri Batygin for their lectures at the United States Particle Accelerator School (USPAS), as well as my instructors at Wheaton College: Darren Craig, Danilo Diedrichs, A. J. Poelarends, Stewart DeSoto, Heather Whitney, and Joshua Whitney. 

Next, I would like to acknowledge the members of the Accelerator Physics Group at the Spallation Neutron Source (SNS). Sarah Cousineau served as my advisor and provided feedback, encouragement, and professional guidance throughout my Ph.D. research. I worked most closely with Nick Evans, who joined me for many problem-solving sessions, provided extensive feedback on my writing and speaking, and allowed me to grow as a researcher. I will always remember our marathon experiments in the SNS control room. I also worked closely with Jeff Holmes, whom I thank for answering many questions about physics and other topics, as well as for his words of encouragement. I also thank Andrei Shishlo and Sasha Zhukov for assistance with the PyORBIT and OpenXAL computer codes, Wim Blockland for assistance with the wire-scanners and target imaging system (and for many free cups of espresso), Charles Peters for leading the setup up the SNS accelerator for our experiments, and Vasiliy Morozov for helpful discussions.

Finally, I could not have completed this dissertation without my family, especially my wife Paris, who provided a steady stream of love and support during the past three and a half years.